Types from data: \textnormal{Making structured data first-class citizens in F\#}

### 2015-11-20 pldi-2016/paper.tex
updates

The provided type is also consistent with our design principles, which prefers optional properties. 
The gain is that the provided types support both open-world data and developer tooling. It is also 
worth noting that our shape inference uses labelled top shapes only as the last resort 
(Theorem~\ref{thm:lub}, \S\ref{sec:impl-hetero}).

@@

Given two ground shapes, the \emph{common preferred shape} relation finds a least upper bound
(Theorem~\ref{thm:lub}). It prefers records, which is important for usability as discussed
earlier.

>>>>

The provided type is also consistent with our design principles, which prefers optional properties. 
The gain is that the provided types support both open-world data and developer tooling. It is also 
worth noting that our shape inference uses labelled top shapes only as the last resort 
(Lemma~\ref{thm:lub}, \S\ref{sec:impl-hetero}).

@@

Given two ground shapes, the \emph{common preferred shape} relation finds a least upper bound
(Lemma~\ref{thm:lub}). It prefers records, which is important for usability as discussed
earlier.
